### 2015-04-24 latex/phd_thesis.tex
Pre-lunch commit. Begin re-write of methsim chapter.

\author{{\bf \Large Peter Francis Hickey}\\\\
Submitted in total fulfilment of the requirements\\
of the degree of Doctor of Philosophy\\\\
April 2015\\\\
Department of Mathematics and Statistics\\
The University of Melbourne\\\\}

@@

@@

\include{introduction} % introduction.tex

@@

>>>>

\author{{\bf \Large Peter Francis Hickey}\\\\
Submitted in total fulfilment of the requirements\\
of the degree of Doctor of Philosophy\\\\
May 2015\\\\
Department of Mathematics and Statistics\\
The University of Melbourne\\\\}

@@

First and foremost, I would like to thank my PhD supervisors, Terry Speed and  Peter Hall. Peter, thank you for supporting my decision to radically change tac very early on in my PhD from a topic in theoretical statistics to a heavily computational and interdisciplinary problem. And Terry, thank you for agreeing to take me on as a student after this change of heart. I have learnt much from working with you and greatly appreciate your generosity and guidance over the course of my PhD. Thanks also to Gordon Smyth, the chair of my PhD committee, for always taking the time to help me.

Thank you to the Walter and Eliza Hall Institute for being such a great place to do research. In particular, thank you to my wonderful friends and colleagues in the Bioinformatics Division for your support and advice. A special thanks to Keith Satterley and the ITS department who put up with and helped fix my computational blunders.

My PhD would not be possible without the people who provided me with data to analyse. I am grateful to Sue Clark, Aaron Statham, Emma Whitelaw and Harry Oey for the opportunity to collaborate with and learn from you. Thanks also to Ryan Lister, Kasper Hansen and Felix Krueger for making their data publicly available and answering all my nit-picky questions. Open science is the best science.

Equally, my PhD would not be possible without the countless people who contribute to the software I use in my daily research. A special thanks to those who helped me as I learnt to write software of my own: Felix Krueger, Toby Sargeant, Martin Morgan, Hervé Pagès, Hadley Wickham and Dirk Eddelbuettel. Open software is the best software.

__software__

__funding, inc. melanie__

- WEHI, Unimelb,
- APA, VLSCI, EMBL, other funders
- Family and friends
- Terry and Peter
- Melanie
- Bioinf division
- Proof readers: Belinda, Saskia, Goknur
- Hannah and Darcy
- Gordon
- Bioconductor, Hadley, Dirk, Felix, Toby
- IT, Keith
- collaborators
- Open access

I am grateful to the Walter and Eliza Hall Institute

@@

@@

\include{concluding_remarks} % concluding_remarks.tex
